---
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(NHANES)
library(nhanesA)
library(glmnet)
library(randomForest)
library(ggplot2)
```



## 17.1.a
```{r, echo = FALSE}
HBV <- nhanes('HEQ_I')

HBAnti <- nhanes('HEPBD_H')

HBSAnti <- nhanes('HEPB_S_H')

Dem <- nhanes('DEMO_H')
```

```{r}
demo_data=Dem[,c(1,13,17)]
demo_data$DMDBORN4[demo_data$DMDBORN4==77|demo_data$DMDBORN4==99]=2
demo_data$DMDEDUC2[demo_data$DMDEDUC2==7|demo_data$DMDEDUC2==9]=1
```

```{r}
label_HBV=HBAnti[!is.na(HBAnti$LBXHBC),][,1:2]
#1 	Positive 		
#2 	Negative
```

```{r}
#Alcohol Use (ALQ_H)
ALQ_H=nhanes("ALQ_H")
#days drink alcohol per wk, mo, yr
drinking_frequency=ALQ_H[,c("SEQN","ALQ120U")]


#Drug Use	DUQ_H
DUQ_H=nhanes("DUQ_H")
#Ever used marijuana or hashish
#1 	Yes	
#2 	No
drug=DUQ_H[,c("SEQN","DUQ200")]
drug$DUQ200[drug$DUQ200==7 |drug$DUQ200==9]=1

#Food Security	FSQ_H
FSQ_H=nhanes("FSQ_H")
#Worried run out of food
out_food=FSQ_H[,c("SEQN","FSD032A")]
out_food$FSD032A[out_food$FSD032A==7|out_food$FSD032A==9|out_food$FSD032A==1|out_food$FSD032A==2]=1

#Health Insurance	HIQ_H
HIQ_H=nhanes("HIQ_H")
#Covered by health insurance
#1 	Yes 
#2 	No
Health_Insurance=HIQ_H[,c("SEQN","HIQ011")]
Health_Insurance$HIQ011[Health_Insurance$HIQ011==7|Health_Insurance$HIQ011==9]=2

#Immunization	IMQ_H
IMQ_H=nhanes("IMQ_H")
#Received Hepatitis B 3 dose series
#1 	Yes at least 3 doses 		
#2 	Less than 3 doses 	
HBV_vaccine=IMQ_H[,c("SEQN","IMQ020")]
HBV_vaccine$IMQ020[HBV_vaccine$IMQ020==7|HBV_vaccine$IMQ020==9|HBV_vaccine$IMQ020==3]=2

#Smoking - Cigarette Use	SMQ_H
SMQ_H=nhanes("SMQ_H")
#Smoked at least 100 cigarettes in life(can't use waking smoke because of too many NAs)
#1 	Yes 	
#2 	No
cigarettes_100=SMQ_H[,c("SEQN","SMQ020")]
cigarettes_100$SMQ020[cigarettes_100$SMQ020==9]=1

#Current Health Status 
HSQ_H=nhanes("HSQ_H")
#general health
general_health=HSQ_H[,c("SEQN","HSD010")]
general_health$HSD010[general_health$HSD010==9|general_health$HSD010==5|general_health$HSD010==-1]=4
general_health$HSD010[general_health$HSD010==1|general_health$HSD010==2]=3
#Housing Characteristics
HOQ_H=nhanes("HOQ_H")
#Home owned, bought, rented, other
#1 	Owned or being bought 
#2 	Rented
home_type=HOQ_H[,c("SEQN","HOQ065")]
home_type$HOQ065[home_type$HOQ065==7|home_type$HOQ065==9|home_type$HOQ065==3]=2
```

```{r}
var_list=c("drinking_frequency","drug","out_food","Health_Insurance","HBV_vaccine","cigarettes_100","general_health","home_type")
HBV_data=label_HBV
for (i in var_list){
  eval(parse(text = paste0("HBV_data=merge(HBV_data,",i,",by='SEQN',all=FALSE)")))
}
```



```{r}
HBV_data=(HBV_data[,-1])
HBV_data_clean <- na.omit(HBV_data)
#HBV_data_factor=as.data.frame(lapply(HBV_data, as.factor))
#HBV_data_factor <- cbind(HBV_data_factor[,1],model.matrix(~., data = HBV_data_factor[,-1])[,-1])


HBV_data_clean[,1]=HBV_data_clean[,1]-1
```



```{r}
set.seed(123)
train_indices <- sample(1:nrow(HBV_data_clean), 0.7 * nrow(HBV_data_clean))
train_data <- HBV_data_clean[train_indices, ]
test_data <- HBV_data_clean[-train_indices, ]


x_train <- as.matrix(train_data[, -1])
y_train <- factor(train_data[,1])
x_test <- as.matrix(test_data[, -1])
y_test <- factor(test_data[,1])


```

```{r}
set.seed(123)
lasso_model <- cv.glmnet(x_train, y_train, alpha = 1,family = "binomial")
lasso_model$lambda.min
lasso_model_fin <- glmnet(x_train, y_train, family = "binomial", alpha = 1, lambda = 0.005)
coef(lasso_model_fin)
```

#lasso:Alcohol Use (ALQ_H)/Drug Use	DUQ_H/Health Insurance	HIQ_H/Smoking - Cigarette Use	SMQ_H

```{r}
set.seed(2024)
HBV_data_clean$LBXHBC=factor(HBV_data_clean$LBXHBC)
rf_model=randomForest(LBXHBC ~ ., data = HBV_data_clean)
importance(rf_model)>median(importance(rf_model))
data_sig=data.frame(factor= rownames(importance(rf_model)),MeanDecreaseGini=importance(rf_model))
ggplot(data_sig,aes(x=factor,y=MeanDecreaseGini))+geom_bar(stat = "identity", fill = "steelblue", width = 0.7)+labs(title = "feature importance (random forest)", x = "factors", y = "MeanDecreaseGini")

```
#random forest:Alcohol Use (ALQ_H)/Food Security	FSQ_H/Health Insurance	HIQ_H/Immunization	IMQ_H

```{r}
#We use the significant feature that at least one method used
#logistics
HBV_data_shrink=HBV_data_clean[,-c(8,9)]
logis_model=glm(LBXHBC~.,data=HBV_data_shrink,family = binomial)
summary(logis_model)
```
We finally use the logistics model to indicate that Drug Use(DUQ_H), Health Insurance	(HIQ_H)/Smoking - Cigarette Use	(SMQ_H) are the most significant features.



#0 	Positive 		
#1 	Negative

#Drug Use	DUQ_H
#Ever used marijuana or hashish
#1 	Yes	
#2 	No

#Health Insurance	HIQ_H
#Covered by health insurance
#1 	Yes 
#2 	No

#Smoking - Cigarette Use	SMQ_H
#Smoked at least 100 cigarettes in life(can't use waking smoke because of too many NAs)
#1 	Yes 	
#2 	No